An Open System for\\ Managing Short Programming Exercises

### 2013-08-08 paper/talk.tex
experiences slide
explanation of what a short exercise is

@@

\begin{itemize}
\item Experiences:
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%% Short Exercises %%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Short Exercises}

\begin{itemize}
  \item Analogy: programming vs.\ learning to play a musical instrument
  \item Larger assignment (like SIGCSE {\em Nifty Assignments}) :: Recital piece
  \item Short exercise :: Playing a scale
\end{itemize}

@@

\begin{itemize}
\item Pilot studies:
  \begin{itemize}
  \item Canisius College: 30 students, CS1, C++
  \item York College: 122 students, CS1, C
  \item Knox College: 23 students, CS1, Java
  \item U.\ of Auckland: 30 students, CS1, C
  \end{itemize}
\item Experiences:
  \begin{itemize}
  \item The software works, students seem to like it
  \item Writing exercises from scratch is hard
  \item Repository has 100+ exercises, but not much reuse has occurred yet
  \end{itemize}
\item Can we scale it to larger courses?
  \begin{itemize}
\item September 2013: U.\ of Auckland: 700 students, CS1, C
  \end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%% Questions %%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Questions}
